Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-23 paper/manuscript.tex
Updating figure 9

    \caption{\textbf{Examples of perturbation networks} (\textbf{A}) Star shaped network with the crystal structure in the center. (\textbf{B}) Network with cycle closures (see more on this in Sec.~\ref{sec:are-they-good}). Arrows indicate the direction of the perturbation. Green cycles indicate good cycle closure, red poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystal structure binding mode.}

@@

    \caption{Alchemical intermediates are created by making the potential energy depend on a an additional variable $\lambda$ that interpolates between the chemical endpoints. In (\textbf{A}), at $\lambda=0$ the molecule is a fully interacting phenol and at $\lambda=1$,  a fully interacting benzene. (\textbf{B}) shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$, intermediates are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$.
    One of the most efficient families of intermediate pathways  are softcore potentials, whose shape is illustrated in (\textbf{C}) with dependence on $\lambda$ and (\textbf{D}) with dependence on the potential energy. Note how when $\lambda$ approaches 0, the energy smoothly approaches zero at all $r$, a necessary requirement for efficient calculations.  }

@@

    U(\vec{r_{ij}},\lambda) = 4\epsilon_{ij} \lambda \left(\frac{1}{(\alpha(1-\lambda) + (r_{ij}/\sigma_{ij})^6)^2} +  \frac{1}{\alpha(1-\lambda) + (r_{ij}/\sigma_{ij})^6}\right)

@@

We have discussed optimal ways of disappearing or appearing Lennard-Jones interaction sites and turning on and off electrostatics terms. What about performing both transformations at the same time? We can't turn off the electrostatics linearly at the same time we turn off the Lennard-Jones terms, as it would leave infinitely large attractive and repulsive electrostatic terms "bare" at small $\lambda$, resulting in the simulation crashing. It \textit{is} possible to apply the same soft core approach to the Coulomb interaction, but it turns out to be somewhat difficult to turn off two soft-core terms simultaneously~\cite{steinbrecher2011softcore}. We therefore recommend performing the transformations in sequence; first, turning off all electrostatics for atoms that must be removed, inserting and removing Lennard-Jones sites (both the insertion and removal can be done simultaneously), and then turning electrostatics for the introduced particles on. However, If there are no removals or introduction to atomic sites, then it is reasonable to change all interactions linearly. 
Other issues, such as whether absolute calculations should retain or remove intramolecular non-bonded interactions, may be less critical and recommendations differ among studies in the literature~\cite{}, and reasonable efficiency can be often obtained with either choice even if some are somewhat better or worse than others. Our recommendation is to leave the intramolecular interactions on during the transformation for simplicity if there are no other known issues with this approach.  The key thing to watch out for is whether the total potential energy, and therefore the intermediate ensembles sampled, change smoothly from beginning to end. If a configurational phase transition is noted in the process (like substantial dihedral rearrangement), then other steps must be taken, perhaps including modifying intramolecular interactions~\cite{???}. These problems can be diagnosed by noticing lack of configuration space overlap between different simulations (see section~\ref{sec:are-they-good})" 
Relative calculations introduce additional choices, including whether to define explicit intermediate states~\cite{} or leave these implicitly defined by the code~\cite{}.
Typically in single topology relative calculations it proves most efficient to first remove electrostatic interactions of any atoms which will be deleted, then modify other non-bonded interactions, then restore electrostatic interactions of any atoms which are being inserted.
Other schemes, such as simultaneously changing electrostatic and Lennard-Jones interactions, even with electrostatic ``soft-core'' potentials~\cite{steinbrecher2007nonlinear}, in our experience typically introduce errors and/or instabilities or are at least unreliable.
It is expected that similar considerations will apply to dualtopology calculations, and the principle of first removing electrostatics and then removing steric interactions will likely serve well.

@@

For BAR/MBAR techniques this means that spacings should typically be equal in [what, variance? ref].
Some schemes to adaptively optimize the spacing of intermediate states based on initial exploratory simulations have been proposed~\cite{}.
An example of this approach for relative binding free energy calculations includes saving configurations from short 10 picosecond simulations starting at $\lambda_0$, and evaluating changes in the standard error of mean (SEM) in $\frac{dU}{d\lambda}$ as reevaluated at new values of $\lambda$, starting with a step size of 0.01 up to a predetermined threshold.
This threshold can be empirically defined as the number of atoms being inserted or deleted in the simulation / 100.
If the absolute value of the difference in SEM is below the defined threshold, then the change in $\lambda$ for re-evaluation of SEM in $\frac{dU}{d\lambda}$ is defined by the current difference in SEM from the threshold divided by the derivative of the SEM with respect to $\lambda$.

@@

There are different easily measurable indicators that can be looked at to test how well converged simulations are and if all alchemical states have been sufficiently sampled for a rigorous analysis. Furthermore, once you have established that individula perturbations are well behaved there are some tricks to ensure the overall perturbation network gives reliable results.

@@

Fig.~\ref{fig:freeenergytrajectories} illustrates how looking at the convergence of your data may be important. In this example the same guest G3 shows different convergence behaviour for two different hosts. CB8 with guest G3 has a longer correlation time than the octa acid (OA) host. In some cases slow correlation time may not be expected and therefore not a feature known in advance. To this end you should always look at all simulation data available check convergence behaviour for each free energy estimate and if need be extend existing simulations or try an approach that requires simulations in two separate binding modes where they interconvert at very slwo timescales.   

@@

    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.

@@

One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespaceb, wu2005phasespacec}. For this purpose, a so-called overlap matrix $\mathcal{O}$ can be used.  $\mathcal{O} \in \mathbb{R}^{K\times K}$, with $K$ being the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates, when using TI. 

@@

Interestingly, as the variance is inversely correlated with the number of states~\cite{klimovich2015guidelines}, it can in principle be reduced below any arbitrary threshold with enough simulation time and a large enough number of $\lambda$ windows. However, decreasing the variance to a value close to 0 is not feasible, as this approach would strongly increase the calculation time. While variance can be decreased both by increasing simulation length and by increasing the number of $\lambda$ values, if overlap is poor, the latter approach often has a larger immediate impact.  Specifically, often the goal is to adjust the $\lambda$ spacing to perform additional sampling in the areas of poor overlap, rather than using arbitrarily spaced windows. Different approaches are described in section~\ref{sec:simulation_protocol_choice}) and more details can be found in the literature~\cite{dakka2018concurrent, hahn2019alchemical}.

@@

This approach may be generalised to sets of connected transformations given the requirement that the sum of free energy changes along edges of a closed cycle should be zero. This analysis is called ``cycle closure''. In practice, such thermodynamic cycles do not actually sum to zero,  and deviations become increasingly large as the size of the cycle increases owing to propagation of error. Though no firm guidelines have emerged, it may be judicious to perform additional configurational sampling along edges of a network that are involved in cycles closing poorly. This may be done by extending simulations duration, or by averaging free energy changes over multiple repeats. The latter approach may yield more reproducible free energy changes, but at the expense of a stronger bias on the estimated free energies due to repeated use of the same input coordinates.
A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a Maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors~\cite{wang2013modeling}. An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node~\cite{mey2016blinded}. Approaches as illustrated by Yang et al. for perturbation map design can also be used to compute relative free energies between target and reference compounds~\cite{yang2020optimal}.

@@

Alchemical free energy calculations have seen a vast increase in popularity also in the pharmaceutical industry for structure based drug discovery~\cite{schindler2020largescale, sherborne2016collaborating, wagner2017computational}. Commercial products such as FEP+ and Flare, which provide a convenient user interface make the setup and use of these methods a lot easier~\cite{wang2015accurate}. Prospective prediction challenges such as the drug design data resource grand challenges provide a community driven platform to evaluate different free energy protocols against each other on unknown targets~\cite{gaieb2018d3r, gaieb2019d3r}. What has come out of these in the past is that SChrödinger's FEP+, performs similar when run by different participant groups~\cite{gaieb2018d3r}, but may not give the desired accuracy with RMSE errors larger than 1 kcal/mol. Other alchemical protocols performed similarly well. We hope that the best practice guide provides a set of tools that allow a better understanding of how to setup, run and interpret alchemical free energy calculations. The choice of the underlying simulation software is left to the user, but hopefully with this guide it is easier to assess whether the generated data is trustworthy or not. 

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to introduction and drug discovery sections, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{} 4.2, 5.3, 6, 8.3.1, 8.3.2\\
\textbf{JDC}: Wrote section~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

@@

Declare any potentially conflicting interests here, whether or not they pose an actual conflict in your view.
MK is employed by Cresset who recently released an commercial tool for performing alchemical free energy calculations.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK acknowledges funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.

>>>>

    \caption{\textbf{Examples of perturbation networks} (\textbf{A}) Star shaped network with the crystal structure in the center. (\textbf{B}) Network with cycle closures (see more on this in Sec.~\ref{sec:are-they-good}). Arrows indicate the direction of the perturbation. Fully converged binding free energy calculations yield binding free energy changes which sum to zero around any closed cycle. However, in practice errors may not sum to zero around closed cycles, providing a way to look for potential sampling problems. Here in (B), green cycles indicate cycles with hypothetically good cycle closure, red those with poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystallographic binding mode.}

@@

    \caption{Alchemical intermediates are created by making the potential energy depend on an additional variable $\lambda$ that interpolates between the chemical endpoints. In (\textbf{A}), at $\lambda=0$ the molecule is a fully interacting phenol and at $\lambda=1$,  a fully interacting benzene. (\textbf{B}) shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$. Intermediates states are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$.
    Softcore potentials provide one of the most efficient families of intermediate pathways, with a $\lambda$ dependence illustrated in (\textbf{C}) and a potential energy dependence shown in (\textbf{D}). Note how as $\lambda$ approaches 0, the energy smoothly approaches zero at all $r$, a necessary requirement for efficient calculations.  }

@@

    U(\vec{r_{ij}},\lambda) = 4\epsilon_{ij} \lambda \left(\frac{1}{(\alpha(1-\lambda) + (r_{ij}/\sigma_{ij})^6)^2} -  \frac{1}{\alpha(1-\lambda) + (r_{ij}/\sigma_{ij})^6}\right)

@@

We have discussed optimal ways of disappearing or appearing Lennard-Jones interaction sites and turning on and off electrostatics terms. What about performing both transformations at the same time? We can't turn off the electrostatics linearly at the same time we turn off the Lennard-Jones terms, as it would leave infinitely large attractive and repulsive electrostatic terms "bare" at small $\lambda$, resulting in the simulation crashing. It \textit{is} possible to apply the same soft core approach to the Coulomb interaction and this is indeed done in a number of implementations, in which case it is important that the Coulomb interaction is softened more rapidly than the Lennard-Jones interaction to avoid charge penetration issues, this can be tricky to ensure for all types of perturbations ~\cite{steinbrecher2011softcore}. A safe but potentially more computationally expensive approach is to perform the transformations in sequence; first, turning off all electrostatics for atoms that must be removed, inserting and removing Lennard-Jones sites (both the insertion and removal can be done simultaneously), and then turning electrostatics for the introduced particles on. Again, If there are no removals or introduction to atomic sites, then it is reasonable to change all interactions linearly. 
Other issues, such as whether absolute calculations should retain or remove intramolecular non-bonded interactions
through either annihilation~\cite{hermans1997inclusion, mann2000modeling, boresch2003absolute, wang2006absoulte, mobley2006use} or decoupling~\cite{fujitani2005direct, mobley2006use} must be considered. Reasonable efficiency can be often obtained with either choice even if some are somewhat better or worse than others although there is not consensus on which is better in all situations. Our recommendation is to leave the intramolecular interactions on during the transformation for simplicity if there are no other known issues with this approach.  The key thing to watch out for is whether the total potential energy, and therefore the intermediate ensembles sampled, change smoothly from beginning to end. These problems can be diagnosed by noticing lack of configuration space overlap between different simulations (see section~\ref{sec:are-they-good})" 
Relative calculations introduce additional choices, such as the order in which to modify nonbonded interactions.
A common process in single topology relative calculations is to first remove electrostatic interactions of any atoms which will be deleted, then modify other non-bonded interactions, then restore electrostatic interactions of any atoms which are being inserted. Although this is a simpler path to understand cognitively and can take advantage of the soft-core potential from eq~\ref{eq:softcore}, this can lead to more intermediate steps and thus be more computationally expensive.
Other schemes, such as simultaneously changing electrostatic and Lennard-Jones interactions with electrostatic ``soft-core'' potentials~\cite{steinbrecher2007nonlinear} may be implemented with fewer intermediate but could require fine-tuning of electrostatic and Lennard-Jones softcore parameters to avoid numerical instabilities. 
At the time of writting, there has not been conclusive evidence to suggest one approach is better in general than the other, so discretion should be left up to the user as to what is viable from both hardware resources, and what the simulation software supports.

@@

For BAR/MBAR techniques this means that state spacing should typically be equal in variance; along a minimal variance path, this is equadistance in $\lambda$, but most paths are not truly minimal variance.~\ref{pham2012optimal, shenfeld2009minimizing}
Some schemes to adaptively optimize the spacing of intermediate states based on initial exploratory simulations have been proposed~\cite{hayes2017adaptive}.

@@

There are different easily measurable indicators that can be looked at to test how well converged simulations are and if all alchemical states have been sufficiently sampled for a rigorous analysis. Furthermore, once you have established that individual perturbations are well behaved, there are some tricks to ensure the overall perturbation network gives reliable results.

@@

Fig.~\ref{fig:freeenergytrajectories} illustrates how looking at the convergence of your data may be important. In this example, the guest G3 shows different convergence behaviour for two different hosts. The CB8 host with guest G3 has a longer correlation time than the octa acid (OA) host. In some cases, slow correlation time may not be expected and therefore not a feature known in advance. To this end, you should always look at all simulation data available check convergence behaviour for each free energy estimate and if need be extend existing simulations or try an approach that requires simulations in two separate binding modes where they interconvert at very slow timescales.   

@@

    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of 5230 ns for OA-G3 and 6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.

@@

One way of assessing reliability of the calculations is checking the phase space overlap between neighboring $\lambda$-windows~\cite{wu2005phasespaceb, wu2005phasespacec}. For this purpose, a so-called overlap matrix $\mathcal{O}$ can be used.  $\mathcal{O} \in \mathbb{R}^{K\times K}$, with $K$ being the number of simulated states, i.e. $\lambda$s. Sufficient overlap is important for reweighting estimators such as BAR or MBAR, but cannot help assess reliability of estimates when using TI. 

@@

Interestingly, as the variance is inversely correlated with the number of states~\cite{klimovich2015guidelines}, it can in principle be reduced below any arbitrary threshold with enough simulation time and a large enough number of $\lambda$ windows. However, decreasing the variance to a value close to 0 is not feasible, as this approach would strongly increase the calculation time. While variance can be decreased both by increasing simulation length and by increasing the number of $\lambda$ values, if overlap is poor, the latter approach often has a larger immediate impact.  Specifically, often the goal is to adjust the $\lambda$ spacing to perform additional sampling in the areas of poor overlap, rather than using arbitrarily spaced windows. Different approaches are described in section~\ref{sec:simulation_protocol_choice} and more details can be found in the literature~\cite{dakka2018concurrent, hahn2019alchemical}.

@@

This approach may be generalised to sets of connected transformations given the requirement that the sum of free energy changes along edges of a closed cycle should be zero. This analysis is called ``cycle closure''. In practice, such thermodynamic cycles do not actually sum to zero,  and deviations become increasingly large as the size of the cycle increases owing to propagation of error. Though no firm guidelines have emerged, it may be judicious to perform additional configurational sampling along edges of a network that are involved in cycles closing poorly. This may be done by extending the duration of simulations, or by averaging free energy changes over multiple repeats. The latter approach may yield more reproducible free energy changes, but at the expense of a stronger bias on the estimated free energies due to repeated use of the same input coordinates.
A scheme to reduce cycle closure errors is used in FEP+ whereby calculated free energy changes along the nodes of the network are re-sampled assuming estimates of the calculated free energy change along a node may be obtained from a Gaussian distribution centered on the estimated free energy change and with a standard deviation equal to the estimated standard deviation of the free energy change. The procedure then uses a maximum likelihood method to find new sets of free energy changes that minimize cycle closure errors~\cite{wang2013modeling}. An alternative approach computes the free energy change between a target and reference compound as a weighted average over all unique paths in the network, with the weights derived from the propagated uncertainties of each node~\cite{mey2016blinded}. Approaches as illustrated by Yang et al. for perturbation map design can also be used to compute relative free energies between target and reference compounds~\cite{yang2020optimal}.

@@

Alchemical free energy calculations have seen a vast increase in popularity also in the pharmaceutical industry for structure based drug discovery~\cite{schindler2020largescale, sherborne2016collaborating, wagner2017computational}. Commercial products such as FEP+ and Flare, which provide a convenient user interface make the setup and use of these methods a lot easier~\cite{wang2015accurate}, but this convenience comes with less flexibility on the simulation protocols. It is also important to understand the current limitations of the methodology to recognise when automated worflow tools can be used effectively for a given protein target. Prospective prediction challenges such as the drug design data resource grand challenges provide a community driven platform to evaluate different free energy protocols against each other on unknown targets~\cite{gaieb2018d3r, gaieb2019d3r}.Such efforts have highlighted that selection of seemingly identical or similar potential energy function or simulation package does not guarantee production of similar free energies owing to differences in simulation protocols. 
(SUGGEST REMOVING THIS SENTENCE What has come out of these in the past is that SChrödinger's FEP+, performs similar when run by different participant groups~\cite{gaieb2018d3r}, but may not give the desired accuracy with RMSE errors larger than 1 kcal/mol. Other alchemical protocols performed similarly well.) We hope that the best practice guide provides a set of tools that allow a better understanding of how to setup, run and interpret reliably alchemical free energy calculations. 

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to introduction and drug discovery sections, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{} 4.2, 5.3, 6, 7.2.3, 8.3.1, 8.3.2, 9\\
\textbf{JDC}: Wrote section~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

@@

Declare any potentially conflicting interests here, whether or not they pose an actual conflict in your view.
MK is employed by Cresset who recently released a commercial tool for performing alchemical free energy calculations.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK and JM acknowledges funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.
